SHIV: Reducing Supervisor Burden using Support Vectors to Efficiently Learn Robot Control Policies from Demonstrations

### 2015-08-23 paper.tex
added Florian and Anca's comments, sensitivity analysis and final grasping in clutter results

@@

\begin{abstract}
Online algorithms for robot model-free imitation learning (such as DAgger) can learn policies for problems where system
dynamics and reward functions are unknown. However, they impose a burden on supervisors to demonstrate labels (control
signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states. SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.  To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.  We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator, 2) 6DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion.  Results suggest that SHIV can learn policies and reduce operator burden significantly  (by a factor of \adnote{fill in}).%[I hope more! - ken]

@@

In \emph{model-free} robot learning from demonstration, a robot learns to perform a task, such as driving or grasping \adnote{we need to put this in fig 1 and refer to it here}, from examples provided by a competent \emph{supervisor}, usually a human. The problem is model-free\adnote{no dynamics model makes it model free, no reward is independent from that; suggest: in such problems, both the ...} if both the system dynamics and the reward function are unspecified, eg. dynamics model may be highly non-linear or noisy and the reward function may trade-off multiple factors and/or depend on future states.  The robot must learn a policy mapping states to actions as it explores new states \adnote{not typical of model free lfd, instead the robot must learn a policy mapping states to actions from the demonstrated examples.}\cite{argall2009survey}.

@@

\emph{On-line}\adnote{inconsistency here beetween offline and on-line instead of online} imitation learning approaches such as DAgger iteratively gather more examples from the supervisor \cite{grollman2007dogged,ross2010efficient,ross2010reduction}. In DAgger, a series of policies are learned.  In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for the  new stats, which are then aggregated with the previous examples for the next iteration. The number of mistakes in DAgger scales linearly with the time horizon \cite{ross2010efficient}. DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.

@@

Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers \cite{hodge2004survey}; or (2) states are in a region that  has been historically misclassified. 
%\adnote{Ken's version below does not seem to represent what we actually do.}
%the action associated with a state under the current policy yield a resulting state that is inconsistent with the expected next state. [how do we measure 2? - Ken]

@@

We compare SHIV with DAgger in three experiments: 1) a driving simulator, 2) 6DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion. Our analysis suggests that compared to DAgger, SHIV learns a policy that performs significantly better given the same amount of human supervision. Conversely, SHIV significantly reduces supervisory burden (by a factor of \adnote{fill in}) while achieving the same performance.

@@

Stream-based active learning has two ingredients: a stream, given here by executing the current best policy, and a query selection method deciding whether or not to query. Typical query selection methods are estimator-centric: they evaluate the estimator's confidence, e.g. distance from the classification hyperplane \cite{tong2002support}, as in Fig. \ref{fig:support_example}(a). An alternative to distance-based measures of confidence is query by committee \adnote{cite}, which uses a committee of hypothesized estimators that are trained on different subsets of the training data. Confidence here is based on the level of agreement or disagreement among these hypotheses, with higher levels of disagreement for a state leading to higher chances of querying that state (Fig. \ref{fig:support_example}(b)).

Both approaches implicitly assume a stationary state distribution --- that the new data is sampled from the same distribution as the previous training data. Although such methods have been previously proposed for online imitation learning (see \cite{chernova2009interactive,grollman2007dogged} for the former and \cite{judah2011active,judah2012active} for the latter),
online imitation learning violates the stationary distribution assumption because each new policy induces a new distribution of states. This can have negative consequences for learning: it has been shown that when training and test distributions are different, query by committee can perform worse than randomly selecting  which states to query \cite{burbidge2007active}.\adnote{merged the two types since they have the same problem, and references the figure}

In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating confidence based on \emph{novelty} (is the state an outlier to the training distribution), as in Fig. \ref{fig:support_example}(c). Additionally, we also assign lower confidence to  historically \emph{mislabeled} regions, as in Fig. \ref{fig:support_example}(d). %Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}. 
Our results in Sec. \ref{}\adnote{fill in} suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector (be it distance or query by committee based).

@@

Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
$\pi_{\theta}$ from time $0$ to time $t-1$.\adnote{shouldnt you then define this above insted of the probability of a trajectory?} This density can be computed by marginalization: $p(\bx_t|\theta) =
\int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction}, we can compute
the average density on states for \emph{any} timepoint by 
\begin{equation}
p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)
\label{eq:density}
\end{equation}

While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_{\bx}|
\bx)$\adnote{this is a typo} or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
Therefore, when 'rolling out' trajectories under a policy
$\pi_{\theta}$, we utilize the robot or a simulator to sample the resulting stochastic trajectories rather than
estimating $p(\bx|\theta)$ itself.

\noindent\textbf{Objective.} Typically, the objective of policy learning is to find a policy that minimizes some known cost function
$C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\tau$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
For example, in task of inserting a peg into a hole, the distance between the peg's current and desired final state can
be considered \cite{levine2015end}.  
In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
a `supervisor' that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$. We are furthermore given
an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
which are the result of the supervisor applying this policy. This induces a training dataset $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories. The goal is to produce a low cost policy for the task based on these demonstrations.

@@

\section{SHIV}
\adnote{putting shiv and dagger side by side. also, notice how I am setting up the rest of the section by explaining what will follow; also, avoid filler sentences like "note that ..." when you are not following that up with a point; avoid filler words like two "basic" steps -- it's just steps, why are they basic?}

Both SHIV and DAgger \cite{ross2010reduction} solve the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1) find an optimal $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states. However, instead of querying the supervisor for every new state, SHIV will actively decide whether the state is risky enough to warrant a query, thereby reducing supervisory burden.

%  \subsection{DAgger: Dataset Aggregation}
% Note that Eq. \ref{eq:LFD_obj} involves both the parameterized policy $\pi_{\theta}$ and the average distribution of
% states with respect to the policy, $p(\bx|\theta)$. Let us recall that Dataset Aggregation (DAgger) is an iterative algorithm developed by \cite{ross2010reduction} which iterates two basic steps for $K$ iterations to find an optimal policy under this objective. 
%DAgger iteratively minimizes $\pi_{\theta}$ on the collected dataset of examples $\mathcal{D}$ and then adds new states
%of high probability under $\pi_\theta$ by sampling via policy `roll outs' from $p(\bx|\theta)$. 
%\fpnote{DAgger and \acro~formal algorithms side by side would be better, also the Step 1/2 below can be
%made more precise then and refer to the algorithm}

\subsection{Step 1.}
The first step of any iteration $k$ is to find a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D_k}=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $D$ from above):
% \fpnote{this is really start of iteration `i', as we circle back}
% At iteration $k=0$ an initial dataset $\mathcal{D}_0$ of $N_0$ supervisor demonstration trajectories 
% with $T+1$ time steps: $\tau^i=(\bx_0^i, \bu_0^i, \ldots, \bx_T^i, \bu_T^i)\in (\mathcal{X}\times\mathcal{U})^{T+1}$ for $i\in \{0, \ldots, N_0\}$
% mapping states to control
% inputs is provided. DAgger solves the following optimization problem with respect to the surrogate loss function:

@@

\adnote{simplified D above to just be pairs so that shiv makes sense too, as it doesnt add full trajectories}
This problem can be treated as a supervised learning problem which can be solved using standard machine
learning techniques, for example a support vector machine or a neural network.

To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$ 
can be considered as present in policy's output. We employ a regularization technique in the optimization which is
used to control the smoothness of the function that is fit to the sampled data. In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.\adnote{is this just us or also dagger?}

 \subsection{Step 2}
The second step starts in both SHIV and DAgger by rolling out the policy $\pi_{\theta_{k}}$ to sample states that are likely to occur under $\theta_{k}$.

@@

Providing correct control inputs or ``labeling'' at each
iteration and each state in DAgger can be tedious, imposing a large burden on the supervisor. \adnote{add in the discussion that another advantage of measuring risk is the early termination which can avoid disaster}
Instead of asking the supervisor for labels at all visited states $\{\bx_0,..,\bx_T\}$, SHIV uses a measure of \emph{risk} to actively \emph{decide} whether a label is necessary. For every state encountered $\bx_t$, it applies a \emph{decision function} $g_{\sigma}$, which we introduce in the next section, parametrized by a risk-sensitivity parameter $\sigma$ which will capture how smooth we expect the policy function to be: smoother functions imply that training examples have larger support, and data nearby will be less risky.

SHIV only asks for supervision on states for which $g(\bx)=-1$: \adnote{don't know what a good way to mention the termination condition is, maybe just a footnote or in discussion at the end as an advantage}
$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\},g(\bx_t)=-1\}$$

@@

Dagger has been experimentally shown to perform well in both simulation and real world
    experiments\cite{}\adnote{cite}. Under a `no regret' assumption, Ross et al.\cite{ross2013learning} furthermore
deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically. For a conservative $\sigma$, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary. However, if $\sigma$ is too high, then SHIV will not collect new data that is needed and revert back to the performance of offline methods. We analyze the dependence on $\sigma$ in our experimental section. Our results suggest that SHIV is robust to this parameter selection. \adnote{must add this experiment!}

\subsection{Measuring Risk}

\adnote{somewhere in this section refer to the second figure}

% However, policy rollouts can in practice result in the robot entering dangerous states. For example, when DAgger was used on a
% quad-copter, the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
We work under the assumption that a state can be risky for 2 reasons: 1) it lies in an area with a low density of
previously trained states, which can cause our policy to mis-predict the supervisor and incur high surrogate
loss \cite{tokdar2010importance}, or 2) the surrogate loss of the current policy at the current state is high, so that the state, although visited, does
not model the supervisor's control inputs correctly.

% To address these limitations, we propose to 1) avoid highly risky states entirely by early termination of the policy
% roll-outs that enter these regions and 2) to recognize non-risky states and to not request supervisor input for these,
% thereby reducing the burden on the human trainer.

%One way to do this is to define risk in terms of distance to a nearest neighbor, but this approach is vulnerable to
%outliers in the known set of states. Another option is to fit a density to the known set of states, which requires an
%exponential number of samples in the dimension of the state space \cite{nadaraya1964estimating}.\adnote{this stuff is in the related work too}

To evaluate risk in high-dimensional state spaces (such as HOG features on images, like in our driving simulator testcase), we use
modified version of the technique known as the One Class SVM that implicitly approximately estimates a boundary of a user defined quantile of
a density representing the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
%\fpnote{Refer to figure, replace "one way to do"  by "an approach to this problem is to" or similar - less informal}

%\subsection{Estimation of Quantile Level Sets}\label{sec:level}
\fpnote{my git commit on this section was overwritten by an old commit at version 10 - reintroduced modifications here,
Michael, please check this is still accurate with recent modifications}
We consider the problem of estimating the quantile level-sets of a distribution $P$ on a set $\mathcal{X}$ by means of a finite set of
independent and identically distributed samples $\mathbf{x}_1,...,\mathbf{x}_n\in \mathcal{X}$.
In most general terms, the quantile function for $P$ and subject to a class of measurable subsets $\mathcal{G}$ of $\mathcal{X}$ is
defined by
\begin{align}\label{eq:quantile}
U(\gamma) = \mbox{inf} \lbrace \lambda(G):P(G) \geq \gamma, G \in \mathcal{G} \rbrace \: 0<\gamma \leq 1
\end{align} 
$\lambda:\mathcal{G}\to \mathbb{R}$ above denotes a volume measure which most commonly is given by the Lebesgue measure.
Suppose furthermore that $G:[0,1]\to \mathcal{G}$ assigns a set $G(\gamma) \in \mathcal{G}$ that attains the infinum
measure (i.e. volume) for each $\gamma\in [0,1]$ (this set is in general not necessarily unique). 
$G(\gamma)$ denotes a set of minimum measure $G \in \mathcal{G}$ with $P(G(\gamma))\ge \gamma$. Note in particular that $G(1)$ is the support of the density $p$ corresponding to $P$, if $p$ exists.

To handle distributions defined on high-dimensional spaces $\mathcal{X}$, work by Scholk{\"o}pf et al. looked at representing the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space \cite{scholkopf2001estimating}. 
By minimizing a support vector regularizer controlling the smoothness of the estimated level set function this work
derives an approximation of the quantile function described in Eq. \ref{eq:quantile}, which in particular has rigorous
convergence guarantees asymptotically when a normalized Gaussian kernel $k$ is chosen and bandwidths decay at an
appropriately chosen rate as the number of samples tends to infinity \cite{vert2006consistency}.
This approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$,
$f_w(\mathbf{x}) = \sum_i w_i k(\mathbf{x}_i, \mathbf{x})$
and $(w,\rho)$ denote the weight vector and offset parameterizing a hyperplane in the feature space associated with a
Gaussian kernel $k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/c}$.

@@

\vspace{-2ex}
\begin{align}\label{eq:decision_func}
g_{\sigma}(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
\end{align}
\adnote{let's make sure we define $\sigma$ above}

@@

\subsection{Car Simulator}
A common benchmark in Reinforcement Learning is the problem of learning a policy for a car to drive around a track
\cite{argall2009survey}. To illustrate our method's ability to scale to high dimensions we use high dimensional HOG features extracted from images
as a state representation.

We implemented a car simulator where the car must follow a polygonal track. If the car accidentally leaves the track, it is placed
back on the center of the track at a nearby position. The car's control input space is given by  $\mathcal{U} = \lbrace
-15^\circ, 0, 15^\circ \rbrace$. A control input instantly changes the angle of the car which drives at a unit speed. 
The internal state space of the car is given by the
xy-coordinates and the angle it is facing. In our experiments, the supervisor is provided by an algorithm that uses
state space search through the driving simulator to plan the next control .

The supervisor drives around the track twice. We collect raw images of the simulation from a 2D bird's eye view
and use Gaussian Pyramids to down-sample the images to $125 \times 125$ RGB pixels and then extract Histogram of
Oriented Gradients (HOG) features using OpenCV. This results in a $27926$ dimensional state space description.
For both DAgger and \acro, we use a Linear Support Vector Machine (SVM) to parameterize allowable
policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
exponential kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution. 
{\color{blue} [-- F: what about $r_0$? --]}

To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane \cite{tong2002support}. The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver. We further compared against Query By Committee, which was trained via bagging \cite{}. Our data set was uniformly divided up into 3 overlapping subsets each with $80\%$ of the data then for each subset a Linear SVM was trained on. If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk. We finally compared our combined risk approach against the traditional One Class SVM without the "hole-punching". We measured the performance in terms of how many states are estimated to be of low risk (i.e. correctly classified) and are of actually high risk on the first policy roll out. Results  are averaged over 50 tracks and shown in Fig. \ref{fig:active_comp}.

>>>>

  \newcommand{\mlnote}[1]{\ifthenelse{\boolean{include-notes}}%
 {\textcolor{purple}{\textbf{ML: #1}}}{}}

@@

\begin{abstract}
Online algorithms for robot model-free imitation learning (such as DAgger) can learn policies for problems where system
dynamics and reward functions are unknown. However, they impose a burden on supervisors to demonstrate labels (control
signals) as the robot encounters new states when iteratively executing its current best policy. We introduce the SHIV
algorithm (Svm-based reduction in Human InterVention), which reduces this burden by enabling the robot to only request supervision for risky states. SHIV uses stream-based active learning with a query selection method that evaluates risk in a manner tailored to non-stationary state distributions.  To facilitate scaling and outlier rejection, risk is based on distance to an approximate level set boundary defined by a One Class support vector machine.  We compare SHIV with DAgger in three policy learning experiments: 1) a driving simulator, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion.  Results suggest that SHIV can learn policies and reduce operator burden significantly  (by a factor of 70$\%$).

@@

In \emph{model-free} robot learning from demonstration, a robot learns to perform a task, such as driving or grasping an object in a cluttered environment as shown in Fig. \ref{fig:teaser}, from examples provided by a competent \emph{supervisor}, usually a human. The problem is model-free if  the system dynamics are unspecified, eg. dynamics model may be highly non-linear or noisy. In learning from demonstration, the cost function is usually unknown or non-continuous and difficult to learn with.  The robot must learn a policy mapping states to controls as it observes the supervisor perform a task\cite{argall2009survey}.

@@

\emph{On-line} imitation learning approaches such as DAgger iteratively gather more examples from the supervisor \cite{grollman2007dogged,ross2010efficient,ross2010reduction}. In DAgger, a series of policies are learned.  In each iteration, the latest policy is "rolled out" (executed) and the supervisor provides demonstrations for the  new states, which are then aggregated with the previous examples for the next iteration. DAgger and related algorithms have been applied in a wide range of applications, from quadrotor flight to natural language to Atari games~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}. Theoretical analysis of DAgger have shown the number of mistakes to scale linearly for strongly convex loss functions.

@@

Risk arises because:  (1) states are different than the states previously encountered and used to generate the current policy, i.e., they can be considered novel or outliers \cite{hodge2004survey}; or (2) states are in a region that  has been historically misclassified, which we know from our training data.
%\adnote{Ken's version below does not seem to represent what we actually do.}
%the action associated with a state under the current policy yield a resulting state that is inconsistent with the expected next state. [how do we measure 2? - Ken]

@@

We compare SHIV with DAgger in three experiments: 1) a driving simulator, 2) 4DOF robot arm push-grasping in clutter (simulation with Box2D), and 3) surgical needle insertion. Our analysis suggests that compared to DAgger, SHIV learns a policy that performs significantly better given the same amount of human supervision. Conversely, SHIV significantly reduces supervisory burden (by a factor of $70\%$) while achieving the same performance.

@@

Stream-based active learning has two ingredients: a stream, given here by executing the current best policy, and a query selection method deciding whether or not to query. Typical query selection methods are estimator-centric: they evaluate the estimator's confidence, e.g. distance from the classification hyperplane \cite{tong2002support}, as in Fig. \ref{fig:support_example}(a). An alternative to distance-based measures of confidence is query by committee  \cite{breiman1996bagging}, which uses a committee of hypothesized estimators that are trained on different subsets of the training data. Confidence here is based on the level of agreement or disagreement among these hypotheses, with higher levels of disagreement for a state leading to higher chances of querying that state (Fig. \ref{fig:support_example}(b)).

Both approaches implicitly assume a stationary state distribution --- that the new data is sampled from the same distribution as the previous training data. Although such methods have been previously proposed for online imitation learning (see \cite{chernova2009interactive,grollman2007dogged} for the former and \cite{judah2011active,judah2012active} for the latter),
online imitation learning violates the stationary distribution assumption because each new policy induces a new distribution of states. This can have negative consequences for learning: it has been shown that when training and test distributions are different, query by committee can perform worse than randomly selecting  which states to query \cite{burbidge2007active}.

In SHIV, we use a query selection method that allows for a non-stationary distribution, evaluating confidence based on \emph{novelty} (is the state an outlier to the training distribution), as in Fig. \ref{fig:support_example}(c). Additionally, we also assign lower confidence to  historically \emph{mislabeled} regions, as in Fig. \ref{fig:support_example}(d). %Our approach builds on the One Class SVM method for approximating quantile level sets \cite{}, which has already been used in novelty detection on high-dimensional image data \cite{}. 
Our results in Sec. \ref{sec:car} suggest that this method is a better predictor of misclassification risk than a typical, estimator-centric query selector (be it distance or query by committee based).

@@

Let $p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
$\pi_{\theta}$ from time $0$ to time $t-1$. This density can be computed by marginalization: $p(\bx_t|\theta) =
\int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction}, we can compute
the average density on states for \emph{any} timepoint by 
\begin{equation}
p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)
\label{eq:density}
\end{equation}

While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_t|
\theta)$ or $p(\bx|\theta)$, we assume that we have a stochastic real robot or a simulator such that for any state
$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ from the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. 
Therefore, when 'rolling out' trajectories under a policy
$\pi_{\theta}$, we utilize the robot or a simulator to sample the resulting stochastic trajectories rather than
estimating $p(\bx|\theta)$ itself.

\noindent\textbf{Objective.} Typically, the objective of policy learning is to find a policy that minimizes some known cost function
$C(\hat{\tau}) = \sum^T_{t=1} c(\bx_t,\bu_t)$ of a trajectory $\hat{\tau}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
For example, in task of inserting a peg into a hole, the distance between the peg's current and desired final state can
be considered \cite{levine2015end}.  
In our learning from demonstration setup, the robot does not have access to the cost function itself. Instead, it only has access to 
a `supervisor' that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\hat{\tau})$. We are furthermore given
an initial set of $N$ stochastic demonstration trajectories $\lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
which are the result of the supervisor applying this policy. This induces a training dataset $\mathcal{D}$ of all state-control input pairs from the demonstrated trajectories. The goal is to produce a low cost policy for the task based on these demonstrations.

@@

\section{SHIV} \label{sec:SHIV}

Both SHIV and DAgger \cite{ross2010reduction} solve the minimization in Eq. \ref{eq:LFD_obj} by iterating two steps: 1) find a $\theta$ using the training data $\mathcal{D}$ thus far, and 2) execute the policy induced by the current $\theta$, and ask for labels for the encountered states. However, instead of querying the supervisor for every new state, SHIV will actively decide whether the state is risky enough to warrant a query, thereby reducing supervisory burden.

\subsection{Step 1.}
The first step of any iteration $k$ is to find a $\theta_k$ that minimizes surrogate loss on the current dataset $\mathcal{D_k}=\{(x_i,u_i)|i\in\{1,\ldots,M\}\}$ of demonstrated state-control pairs (initially just the set $D$ from above):

@@

This problem can be treated as a supervised learning problem which can be solved using standard machine
learning techniques, for example a support vector machine or a neural network.

To handle the fact that the supervisor's policy can be noisy, a zero-mean noise term $\epsilon$ 
can be considered as present in policy's output.  A regularization technique in the optimization is
used to control the smoothness of the function that is fit to the sampled data. In practice this regularization corresponds to a penalty term on either the L2 norm on the weights for regression based techniques or the slack coefficient for support vector machines \cite{scholkopf2002learning}.
 \subsection{Step 2}
The second step starts in both SHIV and DAgger by rolling out the policy $\pi_{\theta_{k}}$ to sample states that are likely to occur under $\theta_{k}$.

@@

Providing correct control inputs or ``labeling'' at each
iteration and each state in DAgger can be tedious, imposing a large burden on the supervisor.
Instead of asking the supervisor for labels at all visited states $\{\bx_0,..,\bx_T\}$, SHIV uses a measure of \emph{risk} to actively \emph{decide} whether a label is necessary. For every state encountered $\bx_t$, it applies a \emph{decision function} $g_{\sigma}$, which we introduce in the next section, parametrized by a risk-sensitivity parameter $\sigma$ which will capture how smooth we expect the policy function to be: smoother functions imply that training examples have larger support, and data nearby will be less risky.

SHIV only asks for supervision on states for which $g(\bx)=-1$:

$$D_{k+1}=\mathcal{D}_k \cup \{(\bx_t,\tilde{\bu_t})\|t\in\{0,\ldots,T\},g(\bx_t)=-1\}$$

@@

Dagger has been experimentally shown to perform well in both simulation and real world
    experiments\cite{NIPS2014_5421,ross2010reduction,ross2013learning}. Under a `no regret' assumption, Ross et al.\cite{ross2010reduction} furthermore
deduced error bounds on the expected loss, which scale linearly in the time horizon $T$ --- as opposed to offline methods which scale quadratically. For a conservative $\sigma$, the SHIV performance is analogous to DAgger without asking the expert when it is absolutely not necessary. However, if $\sigma$ is too high, then SHIV will not collect new data that is needed and revert back to the performance of offline methods. We analyze the dependence on $\sigma$ in Sec. \ref{sec:car}. Our results suggest that SHIV is robust to this parameter selection.

\subsection{Measuring Risk}
% However, policy rollouts can in practice result in the robot entering dangerous states. For example, when DAgger was used on a
% quad-copter, the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
We work under the assumption that a state can be risky for 2 reasons: 1) it lies in an area with a low density of
previously trained states, which can cause our policy to mis-predict the supervisor and incur high surrogate
loss \cite{tokdar2010importance}, or 2) the surrogate loss of the current policy at a state in $\mathcal{D}$ is high, so that the state, although visited, does
not model the supervisor's control inputs correctly.

To evaluate risk in high-dimensional state spaces (such as HOG features on images, like in our driving simulator testcase), we use
a modified version of the technique known as the One Class SVM that  approximately estimates a boundary of a user defined quantile of
a density representing the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
%\fpnote{Refer to figure, replace "one way to do"  by "an approach to this problem is to" or similar - less informal}

%\subsection{Estimation of Quantile Level Sets}\label{sec:level}
We consider the problem of estimating the quantile level-sets of a distribution $P$ on a set $\mathcal{X}$ by means of a finite set of
independent and identically distributed samples $\mathbf{x}_1,...,\mathbf{x}_n\in \mathcal{X}$.
In most general terms, the quantile function for $P$ and subject to a class of measurable subsets $\mathcal{G}$ of $\mathcal{X}$ is
defined by
\begin{align}\label{eq:quantile}
U(\gamma) = \mbox{inf} \lbrace \lambda(G):P(G) \geq \gamma, G \in \mathcal{G} \rbrace \: 0<\gamma \leq 1
\end{align} 
$\lambda:\mathcal{G}\to \mathbb{R}$ above denotes a volume measure which most commonly is given by the Lebesgue measure.
Suppose furthermore that $G:[0,1]\to \mathcal{G}$ assigns a set $G(\gamma) \in \mathcal{G}$ that attains the infinum
measure (i.e. volume) for each $\gamma\in [0,1]$ (this set is in general not necessarily unique). 
$G(\gamma)$ denotes a set of minimum measure $G \in \mathcal{G}$ with $P(G(\gamma))\ge \gamma$. Note in particular that $G(1)$ is the support of the density $p$ corresponding to $P$, if $p$ exists.

To handle distributions defined on high-dimensional spaces $\mathcal{X}$, work by Scholk{\"o}pf et al. looked at representing the class $\mathcal{G}$ via a kernel $k$ as the set of half-spaces in the support vector (SV) feature space \cite{scholkopf2001estimating}. 
By minimizing a support vector regularizer controlling the smoothness of the estimated level set function this work
derives an approximation of the quantile function described in Eq. \ref{eq:quantile}, which in particular has rigorous
convergence guarantees asymptotically when a normalized Gaussian kernel $k$ is chosen and bandwidths decay at an
appropriately chosen rate as the number of samples tends to infinity \cite{vert2006consistency}.
This approach can be thought of as employing $\lambda(G) = ||w||^2$, where $G_w = \lbrace x: f_w(x) \geq \rho \rbrace$,
$f_w(\mathbf{x}) = \sum_i w_i k(\mathbf{x}_i, \mathbf{x})$
and $(w,\rho)$ denote the weight vector and offset parameterizing a hyperplane in the feature space associated with a
Gaussian kernel $k(\bx_0,\bx_1) = e^{-||\bx_0 - \bx_1||^2/2\sigma^2}$.

@@

\vspace{-2ex}
\begin{align}\label{eq:decision_func}
g_{\sigma}(x) = \mbox{sgn}(\langle w,\Phi(x) \rangle-\rho).
\end{align}

@@

\subsection{Driving Simulator} \label{sec:car}
A common benchmark in Reinforcement Learning is the problem of learning a policy for a car to drive around a track
\cite{argall2009survey}. To illustrate our method's ability to scale to high dimensions we use high dimensional HOG features extracted from images
as a state representation.

We implemented a driving simulator where the car must follow a polygonal track. The polygonal tracks are randomly created by sampling from a Gaussian with mean that is the center of the video game workspace.Then a convex hull is computed on the sampled points. In general this produces tracks composed of five to seven edges, an example is shown in Fig. \ref{fig:teaser}(a). If the car accidentally leaves the track, it is placed
back on the center of the track at a nearby position. The car's control input space is given by  $\mathcal{U} = \lbrace
-15^\circ, 0, 15^\circ \rbrace$. A control input instantly changes the angle of the car which drives at a unit speed. 
The internal state space of the car is given by the
xy-coordinates and the angle it is facing. In our experiments, the supervisor is provided by an algorithm that uses
state space search through the driving simulator to plan the next control .

The supervisor drives around the track twice. We collect raw images of the simulation from a 2D bird's eye view
and use Gaussian Pyramids to down-sample the images to $125 \times 125$ RGB pixels and then extract Histogram of
Oriented Gradients (HOG) features using OpenCV. This results in a $27926$ dimensional state space description.
For both DAgger and \acro, we use a Linear Support Vector Machine (SVM) to parameterize allowable
policies $\pi_{\theta}$, with $\gamma=0.01$ as a regularization term on the slack variables, which was set via cross
validation on the initial training examples. For the optimization of Eq. \ref{eq:dual_sup} in \acro, we used an
exponential kernel with a bandwidth of $\lambda=0.01$ and $\nu = 0.95$ to account for $95\%$ of the training distribution.

We compare the policy's performance in terms of minimization of an underlying cost function $c(\bx,\bu)$, which is
defined to be total number of times the car left the track in relation to the number of queries made to the supervisor.
In Fig. \ref{fig:car_cost}, we visualize the performance of DAgger and SHIV.  We run 6 iterations, which is a completion of both Step 1 and Step 2 described in Section \ref{sec:SHIV} of each algorithm over 40 different
randomized polygonal tracks. Figure \ref{fig:car_cost} presents averaged
results from these experiments, suggesting a $70\%$ reduction in the number of queries needed for SHIV compared to DAgger.

\textbf{Comparison to active learning approaches:}
To compare our method against a traditional confidence based active learning approach, we use a confidence measure  of distance from the hyperplane \cite{tong2002support}. The threshold was set to the average distance from the hyperplane for the mis-classified points in $\mathcal{D}_0$, which consisted of two demonstrations from our solver. We further compared against Query By Committee, which was trained via bagging \cite{breiman1996bagging}. Our data set was uniformly divided up into 3 overlapping subsets each with $80\%$ of the data then for each subset a Linear SVM was trained on. If the three classifiers agreed with each other the point was determined low risk and if they disagree it was determined high risk. We finally compared our combined risk approach against the traditional One Class SVM without the "hole-punching". We measured the performance in terms of how many states are estimated to be of low risk (i.e. correctly classified) and are of actually high risk on the first policy roll out. Results  are averaged over 50 tracks and shown in Fig. \ref{fig:active_comp}.

\textbf{Sensitivity Analysis}. 
To analyze the sensitivity of our method we varied the $\sigma$ parameter of the risk estimation function $g_{\sigma}$. SHIV was ran for 6 iterations and averaged over 40 different randomized polygonal tracks. As shown in Table \ref{tab:sens}, small $\sigma$, $\sigma = 1$, corresponds to always asking for help and very large sigma, $\sigma = 350$, relates to  less data being used, but worst performance similar to the traditional supervise learning approach.
